A sheaf--function dictionary for algebraic tori over non-archimedean local fields

### 2013-08-16 shanghai.tex
Expanded abbreviations: PIMS, NSERC, BIRS

We also gratefully acknowledge the financial support of PIMS and NSERC,
and the hospitality of BIRS during our weeklong stay in May 2012.
\David{Should these be abbreviated or written out in full?}

>>>>

We also gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
and of the National Science and Engineering Research Council,
as well the hospitality of the Banff International Research Station during our weeklong stay in May 2012.
